%-------------------------
% Resume in Latex
% Author : J.Kanishkha
% License : MIT
%------------------------

%--- Packages and Functions ----

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
%\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Set the margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

% Set the margins
\geometry{left=0.85cm, top=0.8cm, right=0.85cm, bottom=0.2cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{\vspace{-2pt}}
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProject}[2]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \hspace{-3mm}{#1}:\hspace{1mm} & \hspace*{0pt}\hfill{\footnotesize{ #2}} \vspace{-0.5mm}\\ 
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeLeadership}[3]{
  \item
      \textbf{#1}\\#2 \\
      \textit{\small#3}\\

}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%

\newcommand{\name}{Kanishkha Jaisankar}
\newcommand{\course}{B.E. -Computer Science and Engineering}
\newcommand{\phone}{56 196 4863}
\newcommand{\emaila}{f20190072@dubai.bits-pilani.ac.in}
\newcommand{\github}{jkanishkha0305}
\newcommand{\website}{jkanishkha0305.github.io}
\newcommand{\linkedin}{jkanishkha}



\begin{document}
\fontfamily{cmr}\selectfont


%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{\name}}
\end{center}
\vspace{-4mm}
\begin{center}
    \small{\href{https://github.com/\github}{\faGithub \hspace{0.2mm} \github} |  \href{https://www.linkedin.com/in/\linkedin/}{\faLinkedinSquare \hspace{0.2mm} \linkedin} | 
    \href{https://jkanishkha0305.github.io/Personal_Website/}{\faHome \hspace{0.2mm} \website} |
    \href{mailto:\emaila}{\faEnvelope \hspace{0.2mm} \emaila} | \faPhone \hspace{0.2mm} +971 \phone }
\end{center}
\vspace{-3mm}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Birla Institute of Technology and Science}{Dubai, UAE}
      {Bachelor's of Engineering in Computer Science}{Sep. 2019 -- Aug. 2023}
    \resumeSubheading
      {Chettinad Vidyashram}{Tamilnadu, India}
      {Higher Secondary Education}{Apr. 2017 -- Mar. 2019}
  \resumeSubHeadingListEnd


%-----------Work Experience-----------------
\section{Experience}
  \resumeSubHeadingListStart
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {KPTAC Technologies}{Dubai, UAE}
      {Software Engineering Intern}{Feb. 2023 - Jul. 2023}
      \resumeItemListStart
        \resumeItem{}
          {Performed Web Scraping of e-commerce data from various websites like Carrefour, LuLu, Waitrose using Scrapy framework, Selenium Web Driver and json extraction from hidden Api clients.}
        \resumeItem{}
          {Designed and implemented spiders, item pipelines for automated data extraction, parsing and storing using Scrapy.}
        \resumeItem{}
          {Performed data cleaning and preprocessing to ensure accuracy and consistency of scraped data.}
        \resumeItem{}
          {Performed Data Analysis on cleaned data using PowerBI, pandas, NumPy, Matplotlib}
        \resumeItem{}
          {Worked on medusa.js for headless CMS backend.}
      \resumeItemListEnd

    \resumeSubheading
        {Sentient Labs}{Dubai, UAE}
        {Robotics Engineering Intern}{Jun. 2021 - Aug. 2021}
      \resumeItemListStart
        \resumeItem{}
          {Developed a Robot application using ROS in AWS RoboMaker for obstacle avoidance and path planning.}
        \resumeItem{}
          {Tested the robot application with Turtlebot in a simulation environment using AWS S3 bucket, Gazebo, Rviz.}
        \resumeItem{}
          {Deployed the application to an edge device using AWS Greengrass IOT and established a ROS pipeline using AWS.}
        \resumeItem{}
          {Containerized the robot application with Docker for improved portability and scalability.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

    

%-----------Research Experience-----------------
%\section{Research Experience}


%-----------PROJECTS-----------------
\section{Projects}
 \vspace{-0.4mm}
  \resumeSubHeadingListStart
    \resumeProject{\textbf{\href{https://github.com/Jkanishkha0305/Multi-model-approach-for-autonomous-driving}{Multi-Model approach for Autonomous Driving}}{\hspace{0.2mm} \faGithub}}
	{\raisebox{0.75pt}{Dec. 2022}}
      \resumeItemListStart
        \resumeItem{}
          {Developed Multiple Deep Learning Models to detect and classify Traffic signals, detect obstacles and detect lanes. }
        \resumeItem{}
          {Performed behavioural cloning of self-driving cars in simulated environments using neural networks.}
        \resumeItem{}
          {Performed comparative study with different models like Mask-RCNN, ResNet50, InceptionV3 and MobileNet.}
        \resumeItem{}
          {Designed a self-driving reinforcement learning model using Deep Q-learning in OpenAI Gym environment.}
        \resumeItem{}
          {Built an Autonomous driving vehicle using Jetson Nano, Arduino, Ultrasonic Sensor that can perform Lane Detection, Obstacle Avoidance and response to Traffic Signals using Deep Learning and Image Segmentation.}
      \resumeItemListEnd
 
    \vspace{-15pt}
    \resumeProject{\textbf{\href{https://github.com/Jkanishkha0305/Visual-Tracking-of-Mobile-Robots-using-UAV}{Application of DCNN for Visual Tracking of Mobile Robots using UAV}}{\hspace{0.2mm} \faGithub}}
	{\raisebox{0.75pt}{Dec. 2022}}
      \resumeItemListStart
        \resumeItem{}
          {Developed a Deep learning model to detect the mobile robot by training the model with custom datasets.}
        \resumeItem{}
          {Performed comparative study with different models like Faster-RCNN, SSD, YOLOv5 and YOLOv7 and chose the best-performing model for deployment into the dji Tello drone.}
        \resumeItem{}
          {Used PID controller and OpenCV to autonomously track and follow the mobile robot using dji Tello drone.}

      \resumeItemListEnd
 
    \vspace{-15pt}    
    \resumeProject{\textbf{\href{https://github.com/Jkanishkha0305/Fetal-Health-prediction-from-CTG-Data-using-Ensemble-learning}{Fetal Health prediction from CTG Data using Ensemble learning}}{\hspace{0.2mm} \faGithub}}
	{\raisebox{0.75pt}{Sep. 2022}}
      \resumeItemListStart
        \resumeItem{}
          {Developed an Ensemble learning model to predict the health of the fetus during pregnancy from CTG data.}
        \resumeItem{}
          {Performed ensemble learning through bagging, boosting and majority voting classifiers approaches.}
        \resumeItem{}
          {Machine learning models like XGBoost, Adaboost, RandomForest, Decision Tree, Naive Bayes and  SVM were used.}
        \resumeItem{}
          {1D-CNN and Hybrid CNN+LSTM models were also developed to perform comparative analysis.}
      \resumeItemListEnd
      
    \vspace{-15pt}    
	\resumeProject{\textbf{\href{https://github.com/Jkanishkha0305/Detection-of-Covid-19-from-Chest-Xray-using-Custom-CNN-and-Transfer-Learning}{End-to-End Model to detect Covid-19 from Chest X-ray Images}}{\hspace{0.2mm} \faGithub}}
	{\raisebox{0.75pt}{Mar. 2022}}
      \resumeItemListStart
        \resumeItem{}
          {Developed a Hybrid Learning Model using CNN+LSTM to detect Covid-19 from Chest X-Ray images.}
        \resumeItem{}
          {Performed comparative study of proposed model with different models like Xception, VGG19, MobileNet.}
        \resumeItem{}
          {Developed a web app using HTML, CSS, flask framework and deployed the model in real-time using Heroku.}  
      \resumeItemListEnd
 
    \vspace{-15pt}
        
    %    \resumeProject{\textbf{\href{https://github.com/abxhr/Open-DSA}Open DSA}}
    \resumeProject{\textbf{\href{https://github.com/Jkanishkha0305/ASL-Detection-system-using-Custom-CNN-and-ML-Techniques}{ASL Detection and translation system using Neural Networks}}{\hspace{0.2mm} \faGithub}}
	{\raisebox{0.75pt}{Mar. 2022}}
      \resumeItemListStart
        \resumeItem{}
          {Created a Custom CNN model to detect hand gestures using the American Sign Language system and translate it.}
        \resumeItem{}
          {Performed comparative study across different machine learning models {SVM, LR, KNN, NB, DT} and custom CNN.}
        \resumeItem{}
          {Used the concepts of OpenCV to predict and translate hand gestures from the live video.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-17pt}


%-----------Technical Skills-----------------
\section{Technical Skills}
\vspace{-0.4mm}

\small{
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\hspace{10pt}Languages \ & Python, C++, C, Java, Matlab  \\
\hspace{10pt}Web Technologies & HTML, CSS, Django, Flask, medusa.js\\
\hspace{10pt}ML/AI & TensorFlow, Pytorch, Scikit-learn, OpenCV \\
\hspace{10pt}Data Analytics & Numpy, Pandas, Matplotlib, Seaborn, Plotly, MySQL\\
\hspace{10pt}Cloud Platforms & AWS, Azure, GCP \\
\hspace{10pt}Miscellaneous & Docker, Linux, ROS, Jetson Nano, Arduino, Git, Scrapy\\
\end{tabular}
}

\vspace{-2.5mm}

%-----------Relevant Coursework-----------------
\section{Relevant Coursework}

\small{

{$\bullet$ Data Structures $\bullet$ Foundations of Data Science $\bullet$ Machine Learning $\bullet$ Deep Learning $\bullet$ Artificial Intelligence $\bullet$ Data Mining $\bullet$ Neural Networks \& Fuzzy Logic $\bullet$ Design \& Analysis of Algorithms $\bullet$ Operating Systems  $\bullet$ Compiler Construction $\bullet$ Database Systems $\bullet$ Theory of Computation $\bullet$ Computer Networks $\bullet$ Object Oriented Programming $\bullet$ Discrete Structures $\bullet$ Logic in Computer Science $\bullet$ Computer Architecture $\bullet$ Principles of Programming Languages }\\

}

\vspace{-2.5mm}

%-----------Achievements-----------------
\section{Achievements}

\vspace{1mm}

\small{
    {$\bullet$ Winners of \textit{Dubai World Police Summit 2023} Drone Challenge\textit{, UAE}.}\\
    \vspace{0.5mm}
    {$\bullet$ Shortlisted for finals of the\textit{ Emirates Robotics Competition 2023, Dubai Future Foundation, UAE}.}\\
    \vspace{0.5mm}
    {$\bullet$ Shortlisted for top 20 finalists all over Arab nations in the\textit{ ITAS Arab Youth Competition 2023, Qatar}.}\\
    \vspace{0.5mm}
    {$\bullet$ Winners of \textit{PIED CEL's Desert Hack Startup Competition    2022}.}\\
    \vspace{0.5mm}
    {$\bullet$ Winners of \textit{ACM BPDC’s Capture The Flag (CTF) Competition 2020}.}\\
    \vspace{0.5mm}
    {$\bullet$ Runner-up of \textit{MTC BPDC’s CodeBlitz Competition 2020}.}\\
    \vspace{0.5mm}
    {$\bullet$ Received Academic Scholarship for scoring \textit{9+ GPA in continuous semesters}.}\\
} 

\vspace{-1mm}

%-----------Publications-----------------
\section{Publications}

\vspace{1mm}

\small{
	\textbf{"Classification of Microstructure Images of Metals Using Transfer Learning"}.\textit{MDIS 2022 8th International Conference, Sibiu, Romania, Springer 2022. (Published) \href{https://doi.org/10.1007/978-3-031-27034-5_9}{doi: 10.1007/978-3-031-27034-5}}\\
    \vspace{1mm}
    \textbf{"An End-to-End Hybrid Learning model for detection of Covid-19 from Chest X-ray images"}.\textit{Alliance Technology Conference-1-International Conference on Artificial Intelligence and Applications-2023, Bengaluru, India. (Accepted)}\\
    \vspace{1mm}
    \textbf{"Multi-model approach for autonomous driving: A comprehensive study on traffic sign detection, vehicle detection, lane detection, and deep learning in Udacity Self-Driving Car Simulator"}.\textit{Multimedia Tools and Applications, An International Journal, Springer 2023. (Under Review)}\\
    
}
\vspace{-1.5mm}

%-----------Leadership-----------------
\section{Leadership}

\vspace{0.5mm}

\vspace{-15pt}
\begin{multicols}{3}
	\begin{itemize}
		\resumeLeadership{President}{Aug. 2022 - Present}{IEI BPDC Student Chapter}
		\resumeLeadership{Team Lead}{Jun. 2022 – Present}{Team IFOR and Robotrix}
        \resumeLeadership{Events Executive}{Aug. 2022 - Present}{Flummoxed Quizzing Club}
        \resumeLeadership{Assistant Vice Captain}{Sep. 2022 - Present}{University Cricket Team}
		\resumeLeadership{Technical Executive}{Aug. 2021 - Aug. 2022}{Microsoft Tech Club, BPDC}
		\resumeLeadership{Treasurer}{Aug. 2021 - Jun. 2022}{Flummoxed Quizzing Club}
	\end{itemize}
\end{multicols}

\vspace{-3.5mm}
%-----------Volunteering-----------------
\section{Volunteering}

%\vspace{0.2mm}

\small{
{$\bullet$ Conducted a Hands-on Robotics Workshop on \textit{Arduino, Tinkercad, Microcontrollers, Sensors} and guided the students and faculties to build an \textit{Obstacle Avoidance Robocar} .}\\
{$\bullet$ Conducted a Machine Learning Bootcamp, for high school students during the university STEM event 2021-22.}\\
{$\bullet$ Conducted a 2-day Hands-on Coding Workshop on \textit{HTML, CSS, Javascript, GitHub Basics for university students} .}\\
{$\bullet$ Event Manager for \textit{University Cricket Tournament, University Quiz Fests, STEM event, Spectrum-2022}.}\\
}

\vspace{-2.5mm}

%-----------Certifications----------------
\section{Certifications}

\vspace{-15pt}
\begin{multicols}{3}
	\begin{itemize}
        \resumeLeadership{\href{https://drive.google.com/file/d/1Ie8h6SQCB01rqpMTPAhcZeSxWbhWZ_kK/view?usp=sharing}{Self-Driving Cars Specialization}}{Issued April 2023}{University of Toronto}    \resumeLeadership{\href{https://drive.google.com/file/d/1ntkqytBIRZEXqgHdYQNZMGp1nE3WO55d/view?usp=sharing}{Deep Learning Specialization}}{Issued March 2023}{DeepLearning.AI} \resumeLeadership{\href{https://drive.google.com/file/d/1YZUAKlISMpajxgVp9BG4QAlyjjT0asmS/view?usp=sharing}{Machine Learning Specialization}}{Issued March 2023}{DeepLearning.AI}	\resumeLeadership{\href{https://drive.google.com/file/d/1SjB08sBkOdnVYhFSPnfVwaZvxJDHKTAR/view?usp=sharing}{IBM Data Science Professional}}{Issued September 2022}{IBM} \resumeLeadership{\href{https://drive.google.com/file/d/190uxeWvmM_IX0r2WzYTZ6nSd4hX1L9VZ/view?usp=sharing}{Google Data Analytics Professional}}{Issued August 2022}{Google}
	\end{itemize}
\end{multicols}

%-----------Miscellanous-----------------
\section{Miscellaneous}

\small{
	\textbf{Co-Curricular activities: }{Robotics, Competitive Coding, Cricket, Quizzing, Finance and Investments, Painting, Football. }\\
    \textbf{Languages: }{English, Hindi, Tamil, Telugu, German}\\
}
\end{document}
